---
output:
  pdf_document: 
    keep_md: true
  html_document: default
  md_document:
    variant: markdown_github
urlcolor: blue
geometry: margin=1.5cm
fontsize: 11pt
---
# Tomasz Dworowy

\noindent\makebox[\linewidth]{\rule{\paperwidth}{1pt}}

Email dworowytomasz@gmail.com  
Phone +48 531731238  
[LinkedIn](https://linkedin.com/in/tomasz-dworowy-aab283bb)  
[Hackerrank](https://www.hackerrank.com/dworowytomasz)  
[Github](https://github.com/tdworowy)  

\noindent\makebox[\linewidth]{\rule{\paperwidth}{1pt}}

Software tester, adherent of context driven testing school, specialize in test automation (functional and performance). Professionally interested in DevOps, Agile, data science and machine learning, personally in history, philosophy and economics.   

\noindent\makebox[\linewidth]{\rule{\paperwidth}{1pt}}

# Experience

## Company: Sii  

* Time span: June 2019 - current workplace
* **Position: Test Development Engineer**

### Client: ING Tech Poland

* Time span: May 2020 - current project

#### Project:

Credit cards backoffice application.

#### Responsibilities:

* Test automation with Java
* Testing (GUI, API and data base)

**Tools used**: Java, Oracle SQL Developer, Postman  
**Project Management Methodology**: Scrum.

### Client: Grand parade (William Hill) 

* Time span: October 2019 to March 2020

#### Project:

Data ingestion – goal of project was to prepare data pipeline from mssql, through S3 bucket, to Snowflake database. Pipeline was prepare using Airflow and NiFi.

#### Responsibilities:  

* Test automation with Python and Pytest
* Test case design
* Testing
* Development support  
  
**Tools used**: Python, Pytest, Snowflake, Airflow, Nifi, SQL, Jira, Git, Docker, Terraform  
**Project Management Methodology**: Scrum.

### Client: ABB 

* Time span: July 2019 to September 2019

#### Project:

ServIS 2.0 Proof of technology - goal of project was to test performance of mssql data base (and simple REST api) located in Azure cloud.  

#### Responsibilities:  

* REST api functional testing with Postman
* Data base performance testing with Jmeter
* REST api performance testing with Jmeter
* Preparation of reports with Power BI and Excel  

**Tools used**: Jmeter, Power BI, Postman, Azure, SQL  
**Project Management Methodology**: Scrum.

\noindent\makebox[\linewidth]{\rule{\paperwidth}{1pt}}

## Company: Rockwell Automation  

* Time span: September 2017 – April 2019
* **Position: Software Test Engineer**

#### Projects:

Emulate - Industrial controller emulator, goal of project was to re-use part of industrial controller firmware to prepare emulator for windows 10. Product should be able to emulate multiple controllers as well as communication between them.  

#### Responsibilities:

* Functional testing
* Test automation with Python
* Development of Python API (via NATS) of emulated controller
* Python and C# unit tests
* Tech spikes and documentation
* Jenkins pipeline configuration and maintenance  

**Tools used**: Python, C#, C++, Git, Docker, Jenkins, IBM RQM, google protobuf, NATS message broker  
**Project Management Methodology**: Scrum and SAFe.

\noindent\makebox[\linewidth]{\rule{\paperwidth}{1pt}}

## Company: Alan Systems  

* Time span: December 2013 - September 2017
* **Position: Software Tester**

#### Projects: 
ATMS Watch (12.2013 – 12.2014) - Web time tracking application use to track working time, including time shift, vacations, sick leave etc.  
CREAM (12.2014 – 09.2017) - Customer relationship management web application use to create and coordinate marketing campaigns and to manage customer and products base. 

#### Responsibilities:  

* Functional exploratory testing
* Test automation with selenium webdriver in Java with JUnit
* Automation of rest API tests in Java
* Performance and load tests with Jmeter in Java framework

**Tools used**: Selenium webdriver, Jmeter, Docker, Jenkins, Git, Jira, TestLink, SQL  
**Project Management Methodology**: Scrum.  

\noindent\makebox[\linewidth]{\rule{\paperwidth}{1pt}}

# Education

## University of Economics in Katowice  

* Time span: 2015 – 2018
* The Faculty: Informatics
* Level of education: master
* Specialization: Analysis of large data sets
* Master thesis topic: *Methods, techniques and tools for automated testing in the software development process*

 
## University of Economics in Katowice

* Time span: 2010 – 2013
* The Faculty: Informatics
* level of education: bachelor
* Specialization: Databases and data warehouses
* Bachelor thesis topic: *Suggestions for the use of artificial neural networks in the classification of bonds*

\noindent\makebox[\linewidth]{\rule{\paperwidth}{1pt}}


# Programing languages and skills

``` {r load_libraries, echo=FALSE, warning=FALSE, message=FALSE}
if (!require("radarchart"))
  install.packages("radarchart")
if (!require("webshot"))
  install.packages("webshot")
if (!require("htmlwidgets"))
  install.packages("htmlwidgets")
library(radarchart)
library(webshot)
library(htmlwidgets)
```

```{r Programing, echo=FALSE, fig.height=4}
c <- grDevices::col2rgb(c("blue", "black"))

labs <- c("Python","Java","TypeScript",'R')
scores <- list(
  "Programing languages" = c(9, 6, 5, 4)
 
)
plt <- chartJSRadar(scores = scores, labs = labs, maxScale = 10, colMatrix=c)

saveWidget(plt, "plt1.html")
webshot("plt1.html")

```
```{r skills, echo=FALSE, fig.height=4}
c <- grDevices::col2rgb(c("green", "black"))

labs <- c("Data science", "DevOps","Exploratory testing", "Test automation", "Agile")
scores <- list(
  "Sklis" = c(4, 6, 9, 9, 7)
  
)
plt <- chartJSRadar(scores = scores, labs = labs, maxScale = 10, colMatrix=c)

saveWidget(plt, "plt2.html")
webshot("plt2.html")
```
\newpage

\noindent\makebox[\linewidth]{\rule{\paperwidth}{1pt}}

# Courses

* ISTQB Foundation Level, certificate: 57418
* Machine Learning, Coursera, certificate: [R4LDP4UJKNW5](https://www.coursera.org/account/accomplishments/records/R4LDP4UJKNW5)
* Ancient Philosophy: Aristotle and His Successors, Coursera, certificate: [SJH4XTG8ZC89](https://www.coursera.org/account/accomplishments/records/SJH4XTG8ZC89)
* Kubernetes Essentials, Linux Academy, certificate: [194408](https://linuxacademy.com/profile/u/cert/id/194408)
* Implementing a Full CI/CD Pipeline, Linux Academy, certificate: [197992](https://linuxacademy.com/profile/u/cert/id/197992)
* Learning Full-Stack JavaScript Development: MongoDB, Node, and React, Linkedin
* Introduction to Discrete Mathematics for Computer Science (specialization), Coursera, certificate: [SB2ADSZH9GXJ](https://www.coursera.org/account/accomplishments/specialization/SB2ADSZH9GXJ)
* Introduction to Complexity, Santa Fe Institute(complexityexplorer.org), certificate:[226951170](https://www.complexityexplorer.org/courses/104-introduction-to-complexity/certificates/226951170)
* Data Science: Foundations using R (specialization), Coursera, certificate: [KH2HS2XGHY27](https://www.coursera.org/account/accomplishments/specialization/KH2HS2XGHY27)

\noindent\makebox[\linewidth]{\rule{\paperwidth}{1pt}}

# Influenced by books

* *Lessons Learned in Software Testing*, Cem Kaner, James Bach, Bret Pettichord
* *Explore It!*, Elisabeth Hendrickson 
* *Clean Code*, *Clean Coder* and *Clean Architecture*”, Robert C. Martin
* *Thinking, Fast and Slow*, Daniel Kahneman
* *The Systems Bible: The Beginner's Guide to Systems Large and Small*, John Gall
* *How Not to Be Wrong: The Power of Mathematical Thinking*, Jordan Ellenberg 
* *The Black Swan*, Nassim Nicholas Taleb

\noindent\makebox[\linewidth]{\rule{\paperwidth}{1pt}}


\scriptsize Wyrażam zgodę na przetwarzanie moich danych osobowych dla potrzeb niezbędnych do realizacji procesu rekrutacji zgodnie z Rozporządzeniem Parlamentu Europejskiego i Rady (UE) 2016/679 z dnia 27 kwietnia 2016 r. w sprawie ochrony osób fizycznych w związku z przetwarzaniem danych osobowych i w sprawie swobodnego przepływu takich danych oraz uchylenia dyrektywy 95/46/WE (RODO).\par